\typeout{IJCAI-18 Instructions for Authors}

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage{ijcai18}

\usepackage{times}
\usepackage{xcolor}
\usepackage{soul}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}

\title{Poker Project - Team \#23}

\author{
Au Liang Jun, David Goh Zhi Wei, Law Yong Qiang Clinton, Lee Yiyuan, Tan E-Liang
\\ 
National University of Singapore
}
\begin{document}

\maketitle

\section{Introduction}
This section should introduce the problem we are considering, together with a rough overview of our approach, and a summary of our results. It should also contain a rough summary of what to expect in each of the subsequent sections.

\section{Agent Design}
This section should contain information about how our agent makes decisions. Minimax, heuristics, etc.

\section{Agent Training Methodology}
\subsection{David's Leaderboard Approach}
Intuition, justification, details.

\subsection{CMA-ES Approach}
Intuition, justification, details.

\subsection{PSO Approach} 
Intuition, justification, details.

\subsection{Agent Training Framework}
Details about how we monopolized entire clusters. Optimization tweaks (e.g. fast monte-carlo, Cython). Speedups achieved solely within training framework should be contained here, and not in training results.

\section{Training Results}
Performance (strength of trained players, convergence of training, etc) of agent designs/training. Uptime on CS3243's leaderboard.

\section{Conclusion and Further Work}
Summary of approach, implementation details. Thoughts and further work. Acknowledgements (maybe).

\bibliographystyle{named}
\bibliography{ijcai18}

\end{document}

